Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-09-03 bbbq_article.tex
Better tables

\begin{figure}[!htbp]
  \includegraphics[width=0.9\textwidth]{ic50s_per_haplotype/ic50s_per_haplotype.png}
  Distribution of predicted IC50s (in nM) per haplotype
  \label{fig:ic50s_per_haplotype}
\end{figure}

\begin{table}[!htbp]
  \input{ic50s_per_haplotype/ic50s_per_haplotype.latex}
  \caption{
    Predicted IC50s (in nM) per haplotype
    \richel{Used randomly simulated peptides, results are real}
  }
  \label{table:ic50s_per_haplotype}
\end{table}

>>>>

% Less pretty 
% 
% \begin{figure}[!htbp]
%   \includegraphics[width=0.9\textwidth]{ic50s_per_haplotype/ic50s_per_haplotype.png}
%   \caption{
%     IC50 values that define a binder
%   }
%   \label{fig:ic50s_per_haplotype}
% \end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=0.9\textwidth]{ic50s_per_haplotype/ic50s_per_haplotype_per_mhc_class.png}
  \caption{
    IC50 values that define a binder
  }
  \label{fig:ic50s_per_haplotype}
\end{figure}

\input{ic50s_per_haplotype/ic50s_per_haplotype_1.latex}

\input{ic50s_per_haplotype/ic50s_per_haplotype_2.latex}
